IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/appendix.tex
start of clearance in appendix

>>>>

We also give details for the clearance extension below.

\subsection{Clearance}

As we have outlined in Section~\ref{sec:clearance}, we first extend
tasks with an additional label |ilc|, which corresponds to the
clearance of that task, and provide two primitives to read and
write that value:
\[ |fullconfc id il ilc tS ie| \]

\begin{figure}
  %{
  %format .->  = "\overset{\alpha}{\hookrightarrow}"
  %format .-/>  = "\not\overset{\alpha}{\hookrightarrow}"
  \begin{code}
    ie  ::= cdots | getClearance | setClearance ie
    iE  ::= cdots | setClearance iE
  \end{code}
  \begin{mathpar}
      \inferrule[I-getClearance]
      { }
      {|
        niconf iS id il ilc getClearance
        ->
        niconf iS id il ilc ilc
        |}

      \and
      \inferrule[I-setClearance]
      { }
      {|
        niconf iS id il ilc (setClearance ilc')
        ->
        niconf iS id il ilc' unit
        |}
  \end{mathpar}
  \caption{Syntax and semantics for clearance.  These rules are
    understood to be an addition to the existing rules given earlier,
    except for the \textsc{I-sandbox} rule, which replaces the previous
    one.
    All existing rules do not modify the clearance.}
  \label{fig:clearance}
  %}
\end{figure}
